Towards Automated Refactoring of Code Clones in Object-Oriented Programming Languages

### 2019-09-19 sattose/paper.tex
Updates from Overleaf

\title{Towards Automated Refactoring of Code Clones in Object-Oriented Programming Languages\\- Work in Progress -}

\author{
Simon Baars \\ University of Amsterdam\\
                Amsterdam, Netherlands \\ simon.mailadres@gmail.com
\and
Ana Oprescu \\ University of Amsterdam\\
                Amsterdam, Netherlands \\
                AM.Oprescu@uva.nl
}

@@

\section{Conclusion and next steps}\label{chap:conclusion}
In the research we have conducted so far we have made three novel contributions:
\begin{itemize}
    \item We proposed a method with which we can detect clones that can/should be refactored.
    \item We mapped the context of clones in a large corpus of open source systems.
    \item We mapped the opportunities to perform method extraction on clones this corpus.
\end{itemize}

@@

The research that we have conducted so far analyzes the context of different kinds of clones and prioritizes their refactoring. Firstly, we looked at the inheritance relation of clone instances in a clone class. We have found that a little more than a third of all clone classes are flagged unrelated, which means that they have at least one instance that has no relation through inheritance with the other instances. About a third of the clone classes all of its instances are in the same class.

>>>>

\title{Towards Automated Refactoring of Code Clones in Object-Oriented Programming Languages}

\author{
Simon Baars \\ University of Amsterdam\\
                Amsterdam, Netherlands \\ simon.mailadres@gmail.com
\and
Ana Oprescu \\ University of Amsterdam\\
                Amsterdam, Netherlands \\
                A.M.Oprescu@uva.nl
}

@@

\section{Conclusion and next steps}\label{chap:conclusion}
In this research we made three novel contributions:
\begin{itemize}
    \item We proposed a method with which we can detect clones that can/should be refactored.
    \item We mapped the context of clones in a large corpus of open source systems.
    \item We mapped the opportunities to perform the ``Extract Method'' refactoring technique on clones this corpus.
\end{itemize}

@@

We analyzed the context of different kinds of clones and prioritized their refactoring. Firstly, we looked at the inheritance relation of clone instances in a clone class. We found that a little more than a third of all clone classes are flagged unrelated, which means that they have at least one instance that has no relation through inheritance with the other instances. For about a third of the clone classes all of their instances are in the same class.
